\pdftitle

### 2017-05-16 maxNt.tex
worked on Intro

Recent advances in electrophysiological techniques allow to
record from large population of neurons [\cite]. The recorded neurons
are usually picked out from a specific area according to an unknown process, and from their
observation in relation to stimuli or behavioral task, we strive for
understanding the mechanism behind neuronal coding. That is, they are assumed to be a
\enquote{representative random sample} of the neurons in that area.

>>>>

Recent advances in electrophysiological techniques allow to
record from large population of neurons [\cite]. The recorded neurons
are usually picked out from a specific brain area according to an unknown process, and from their
observation in relation to stimuli or behavioral task, we strive for
understanding the mechanism behind neuronal coding. That is, they are assumed to be a
\enquote{representative random sample} of the neurons in that area.
